An agent-based model for city networks based on interactions between firms

### 2019-10-01 slides.tex
.

\sframe{Urban Firm linkages and geo-economic processes}{

@@

How can we capture geographical and economic processes within urban networks of firms with a generative model?

}
\sframe{Towards a generative model of urban firm networks}{

Towards a generative model of urban firm networks

% research question / objective
% ???

@@

\textbf{Model parameters: } $\gamma_F, \gamma_T, \gamma_W, \gamma_S, \gamma_D = \frac{1}{d_G}, \gamma_G = \frac{1}{d_G}$

@@

\tiny

\begin{enumerate}
    \item Generate $N \textrm{ = } 700$ cities with size following a power law $E_i \textrm{ = } E_0 \cdot i^{-\alpha}$ with $E_0 \textrm{ = } 10^{11}$ and $\alpha=1.1$ (computed on Europe for GDP with cities larger than 50.000 inhabitants)
    \item Distribute them randomly in space (\cite{simini2019testing} vs \cite{banos2011christaller})
    \item Create countries with k-means clustering ($C \textrm{ = } 30$)
    \item Distribute sectors such that (i) smaller cities are more specialized and (ii) larger cities are more knowledge-based, with a one dimensional axis to position sectors $1/K \ldots 1$ where the density $f\left(k\right)$ follows a log-normal with $\left(\mu,\sigma\right)$ such that $\sqrt{\Var f} = K/2$ for the largest, $\sqrt{\Var f} = 1/K$ for the smallest
\end{enumerate}

@@

@@

@@

\begin{itemize}
	\item Current experiment: only network dynamics (short time scale)
	\item One-factor sampling with 100 repetitions to assess statistical properties
	\item Grid sampling with 20 repetitions for model behavior (2years 5month of computation)
\end{itemize}

@@

    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-highgravity_seed-12102_t1500.png}\hspace{0.1cm}
    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-lowgravity_seed-12102_t1500.png}

@@

	\textit{Networks at $t = 1500$, for default parameters values and high gravity (left) and low gravity (right)}

@@

    \includegraphics[width=0.48\textwidth]{figures/internationalization-gravityDecay_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figures/rhoDegreeSize-gravityDecay_errorbars.png}
}

% alors la je ne comprend pas desolee l'interpretation de l'evolution des courbes, l'internationalisation (qui est defini par la modularite diminue avec le temp?
% et le p(di,E) proba entre distance et poids economique? comment tu interpretes ca? il y a un seuil a la fin
% du coup je ne comprend pas bien comment interpreter

>>>>

\sframe{Urban firm linkages and geo-economic processes}{

@@

$\rightarrow$ \textit{How can we capture geographical and economic processes within urban networks of firms with a generative model?}

\begin{itemize}
	\item Indirect inference on processes
	\item Includes path-dependency
\end{itemize}

@@

\textbf{Model parameters: } $\gamma_F, \gamma_T, \gamma_W, \gamma_S, \gamma_D \textrm{ = } \frac{1}{d_G}, \gamma_G \textrm{ = } \frac{1}{d_G}$

@@

\footnotesize

\begin{enumerate}
    \item Generate $N \textrm{ = } 700$ cities with size following a power law $E_i \textrm{ = } E_0 \cdot i^{-\alpha}$ with $E_0 \textrm{ = } 10^{11}$ and $\alpha \textrm{ = } 1.1$ (computed on Europe for GDP with cities larger than 50.000 inhabitants)
    \item Distribute them randomly in space (\cite{simini2019testing} vs \cite{banos2011christaller})
    \item Create countries with k-means clustering ($C \textrm{ = } 30$)
    \item Distribute sectors such that (i) smaller cities are more specialized and (ii) larger cities are more knowledge-based, with a one dimensional axis to position sectors $1/K \ldots 1$ where the density $f\left(k\right)$ follows a log-normal with $\left(\mu,\sigma\right)$ such that $\sqrt{\Var f} \textrm{ = } K/2$ for the largest, $\sqrt{\Var f} \textrm{ = } 1/K$ for the smallest
\end{enumerate}

@@

\textbf{Implementation}

@@

\textbf{Experiments}

@@

\begin{itemize}
	\item Current experiment: only network dynamics (short time scale)
	\item One-factor sampling with 100 repetitions to assess statistical properties
	\item Grid sampling with 20 repetitions for model behavior (2years 5months of computation)
\end{itemize}

@@

    \begin{center}
    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-highgravity_seed-12102_t1500.png}\hspace{0.1cm}
    \includegraphics[width=0.48\textwidth]{figures/ex_alleq-lowgravity_seed-12102_t1500.png}
	\end{center}

@@

	\textit{Networks at $t \textrm{ = } 1500$, for default parameters values and high gravity (left) and low gravity (right)}

@@

    \includegraphics[width=0.48\textwidth]{figures/internationalization-gravityDecay_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figures/rhoDegreeSize-gravityDecay_errorbars.png}

    \footnotesize

    \textit{(Left) Internationalization index decreases exponentially with gravity decay; (Right) Correlation between }

% alors la je ne comprend pas desolee l'interpretation de l'evolution des courbes, l'internationalisation (qui est defini par la modularite diminue avec le temp?
% et le p(di,E) proba entre distance et poids economique? comment tu interpretes ca? il y a un seuil a la fin
% du coup je ne comprend pas bien comment interpreter
%  => c'est pas dans le temps, c'est en fonction du parametre de gravity ; internationalization comme c'est la modularite elle est minimisee plus c'est internataional
